Reanalysis Step 5: Sensitivity Analysis with E-values

### 2025-08-20 reanalysis-5-sensitivity.qmd
file name

# Create summary table
evalue_summary_main <- data.frame(
  Effect = "Main Effect (Lapsing)",
  OR = round(or_main, 3),
  CI_Lower = round(ci_lower_main, 3),
  CI_Upper = round(ci_upper_main, 3),
  E_Value_Point = round(evalue_main$est.Evalue, 3),
  E_Value_CI = round(evalue_main$lower.Evalue, 3)
)

@@

**Interpretation:** `r if(evalue_main$est.Evalue > 2) paste0("The E-value of ", round(evalue_main$est.Evalue, 2), " suggests that unmeasured confounding would need to be relatively strong to explain away the observed association.") else if(evalue_main$est.Evalue > 1.5) paste0("The E-value of ", round(evalue_main$est.Evalue, 2), " suggests moderate robustness to unmeasured confounding.") else paste0("The E-value of ", round(evalue_main$est.Evalue, 2), " suggests the finding could be sensitive to unmeasured confounding.")`

@@

  evalue_results[[i]] <- data.frame(
    DR_Severity = subgroup$DR_Severity,
    Treatment = subgroup$Treatment,
    OR = round(or_val, 3),
    CI_Lower = round(ci_lower, 3),
    CI_Upper = round(ci_upper, 3),
    E_Value_Point = round(evalue$est.Evalue, 3),
    E_Value_CI = round(evalue$lower.Evalue, 3)
  )
}

@@

evalue_comparison <- data.frame(
  Assumption = c("Rare Outcome (<10%)", "Common Outcome"),
  E_Value_Point = c(evalue_main$est.Evalue, evalue_common$est.Evalue),
  E_Value_CI = c(evalue_main$lower.Evalue, evalue_common$lower.Evalue)
)

@@

**Main Findings:**  
- Overall E-value: `r round(evalue_main$est.Evalue, 2)`  
- Range of subgroup E-values: `r round(min_evalue, 2)` to `r round(max_evalue, 2)`

>>>>

# Create summary table
# evalues.OR returns a matrix with rows "RR" and "E-values"
evalue_point <- evalue_main["E-values", "point"]
evalue_ci <- evalue_main["E-values", "lower"]

evalue_summary_main <- data.frame(
  Effect = "Main Effect (Lapsing)",
  OR = round(or_main, 3),
  CI_Lower = round(ci_lower_main, 3),
  CI_Upper = round(ci_upper_main, 3),
  E_Value_Point = round(evalue_point, 3),
  E_Value_CI = round(evalue_ci, 3)
)

@@

**Interpretation:** `r if(evalue_point > 2) paste0("The E-value of ", round(evalue_point, 2), " suggests that unmeasured confounding would need to be relatively strong to explain away the observed association.") else if(evalue_point > 1.5) paste0("The E-value of ", round(evalue_point, 2), " suggests moderate robustness to unmeasured confounding.") else paste0("The E-value of ", round(evalue_point, 2), " suggests the finding could be sensitive to unmeasured confounding.")`

@@

  evalue_results[[i]] <- data.frame(
    DR_Severity = subgroup$DR_Severity,
    Treatment = subgroup$Treatment,
    OR = round(or_val, 3),
    CI_Lower = round(ci_lower, 3),
    CI_Upper = round(ci_upper, 3),
    E_Value_Point = round(evalue["E-values", "point"], 3),
    E_Value_CI = round(evalue["E-values", "lower"], 3)
  )
}

@@

evalue_comparison <- data.frame(
  Assumption = c("Rare Outcome (<10%)", "Common Outcome"),
  E_Value_Point = c(evalue_main["E-values", "point"], evalue_common["E-values", "point"]),
  E_Value_CI = c(evalue_main["E-values", "lower"], evalue_common["E-values", "lower"])
)

@@

**Main Findings:**  
- Overall E-value: `r round(evalue_point, 2)`  
- Range of subgroup E-values: `r round(min_evalue, 2)` to `r round(max_evalue, 2)`
